Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-09-06 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:09:05	19:04:33	(Sat 5.Sep)
la2pdf commit - 2015:09:06	13:33:56	(Sun 6.Sep)

In short, our findings show that when applied to experimental data, the weights chosen by a robustified MVDR yield responses that tend to be symmetric and steered within a fraction of the -3dB resolution of the respective window. When mimicking these responses with Kaiser windows, we obtain images with both improved noise suppression and resolution. We resolution gain can be made predictable and depending on the amount of steering we apply to the windows. Overall, the image quality produced by LCA is comparable to MVDR, and sometimes even better. LCA is also inherently robust, easy to implement and fairly easy to understand.

@@

\begin{figure}[tbp]%
\includegraphics[width=\linewidth]{gfx/cross_tagged.png}%
\caption{The cross and accompanying anchor used to test the beamformers.}\label{cross}
\end{figure}

@@

\begin{figure*}[t]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds_lca_windows_beta.pdf}%
\caption{$\beta$-values of the windows LCA selects for each image pixel. The underlying image is the one shown in \Fig{oversampling_mosaic_bounds}, with the same parameters. The location of the anchor and cut line marked in red. Note how LCA prefers a rectangular window ($\beta=0$) on the anchor. }\label{oversampling_mosaic_bounds_beta}
\end{figure*}

@@

\begin{figure*}[t]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic.pdf}%
\caption{LCA images using window sets with varying parameter boundaries. Oversampled image, 19x20 windows.}\label{oversampling_mosaic}
\end{figure*}

>>>>

Our findings show that when applied to experimental data, the weights chosen by a robustified MVDR yield responses that tend to be symmetric and steered within a fraction of the -3dB resolution of the respective window. When letting LCA choose from Kaiser windows with similar responses, we obtain images with both improved noise suppression and resolution. The resolution gain can be made predictable and depending on the amount of steering we apply to the windows. Overall, the image quality produced by LCA is comparable to MVDR, and sometimes even better. LCA is also inherently robust, easy to implement and fairly easy to understand.

@@

\begin{figure}[tbp]%
\includegraphics[width=\linewidth]{gfx/cross_tagged.png}%
\caption{One of the objects used to test the beamformers is a 1\,m long cross attached to an anchor with a diameter of 13\,cm.}\label{cross}
\end{figure}

@@

\begin{figure*}[t]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds_lca_windows_beta.pdf}%
\caption{$\beta$-values of the windows LCA selects for each image pixel. The underlying image is the one shown in \Fig{oversampling_mosaic_bounds}, with the same parameters. The location of the anchor and cut line is marked in red. Note how LCA prefers a rectangular window ($\beta=0$) on the anchor.}\label{oversampling_mosaic_bounds_beta}
\end{figure*}

@@

\begin{figure*}[t]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic.pdf}%
\caption{LCA images using different window database sizes. The window boundaries are the same.}\label{oversampling_mosaic}
\end{figure*}
